# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
```{r loaddata}
unzip(zipfile="activity.zip")
data <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?
```{r}
library(ggplot2)
activity_steps <- aggregate(steps ~ date, activity_na, sum)
hist(activity_steps$steps, col=2, main="Histogram of total number of steps per day", 
xlab="Total number of steps in a day")
summary(activity_steps)
```

## What is the average daily activity pattern?
```{r}
library(ggplot2)
activity_na_stps_day<-aggregate(steps ~ date, activity_na, sum)
head(activity_na_stps_day)
hist(activity_na_stps_day$steps, main="Histogram of total number of steps per day (imputed)", 
     xlab="Total number of steps in a day")
mean(activity_na_stps_day$steps)
median(activity_na_stps_day$steps)

```

On average across all the days in the dataset, the 5-minute interval contains
the maximum number of steps?
```{r}
activity_max_stps<-which.max(activity_interval$steps)
activity_interval[activity_max_stps,]

```

## Imputing missing values

```{r how_many_missing}
sum(is.na(activity))
activity_na<-activity
activity_na_stps_day<-aggregate(steps ~ date, activity_na, sum)
```

All of the missing values are filled in with mean value for that 5-minute
interval.

```{r}
# Replace each missing value with the mean value of its 5-minute interval
activity_na<-activity
activity_na['date_type']<-weekdays(as.Date(activity_na$date))
activity_na$date_type[activity_na$date_type %in% c('Saturday','Sunday') ] <- "weekend"
activity_na$date_type[activity_na$date_type!= "weekend"] <- "weekday"
activity_na$day_type <- as.factor(activity_na$day_type)

```
Histogram of the total number of steps taken each day and calculate the mean and median total number of steps.

```{r}
intvl_steps_imputed <- aggregate(steps ~ interval+day_type, activity_na, mean)
library(ggplot2)
qplot(interval, steps, data=intvl_steps_imputed, type='l', geom=c("line"), xlab="Interval", 
      ylab="Number of steps", main="") + facet_wrap(~ day_type, ncol=1)
```

